### 2016-06-29 GPCE2016/sections/Introduction.tex
revise. fixed comments by Marco.
merge

Object interfaces
provide support for automatic type-refinement.
In contrast, in CB 
special care and verbose explicit type-refinement is be required to
produce code that deals with subtyping adequately.

  We believe that such verbosity hindered and slowed
down the discovery of useful programming patterns involving
type-refinement. A recently discovered
solution~\cite{eptrivially} to the Expression
Problem~\cite{wadler98expression} in Java-like languages, shows how easy it is to solve
the problem using only type-refinement. However it took nearly 20
years since the formulation of the problem for that
solution to be presented in the literature. In IB, due to
its emphasis on type-refinement, that solution should have been much
more obvious.

@@

Another advantage of IB is its support for
multiple inheritance. The literature is rich on how
easy it is to combine multiple sources of pure behaviour,
using mechanisms such as traits~\cite{scharli03traits}. In Java
multiple \emph{interface} inheritance has been supported since
inception, and in Java 8 default methods~\cite{goetz12fdefenders} bring some of the
advantages of traits into Java. In contrast, the literature~\cite{Sak89dis,bracha90mixin,malayeri2009cz}
is also rich on how hard it is to modularly combine multiple sources
of behaviour \textbf{and} state with multiple \emph{implementation}
inheritance of classes. In IB there is only multiple
interface inheritance, yet programmers can still use state via 
abstract state operations. IB enables powerful
idioms using multiple inheritance and state.

>>>>

Object interfaces provide support for automatic type-refinement.  In
contrast, in CB special care and verbose explicit type-refinement is
required to produce code that deals with subtyping adequately. We
believe that such verbosity hindered and slowed down the discovery of
useful programming patterns involving type-refinement. A recently
discovered solution~\cite{eptrivially} to the Expression
Problem~\cite{wadler98expression} in Java-like languages, shows how
easy it is to solve the problem using only type-refinement. However it
took nearly 20 years since the formulation of the problem for that
solution to be presented in the literature. In IB, due to its emphasis
on type-refinement, that solution should have been more obvious.

@@

Another advantage of IB is support for
multiple inheritance. The literature is rich on how
easy it is to combine multiple sources of pure behaviour,
using mechanisms such as traits~\cite{scharli03traits}. In Java
multiple \emph{interface} inheritance has been supported since
inception, and Java 8 default methods~\cite{goetz12fdefenders} bring some of the
advantages of traits to Java. The literature~\cite{Sak89dis,bracha90mixin,malayeri2009cz}
is also rich on how hard it is to combine multiple sources
of behaviour \textbf{and} state with multiple \emph{implementation}
inheritance of classes. In IB there is only multiple
interface inheritance, yet programmers can still use state via 
abstract state operations. IB enables powerful
idioms using multiple inheritance and state.
